EXAM Fits and Predictions

### 2023-11-14 Simulations/htw_exam.qmd
improve model tables with flextable

```{r}
# load and view data
pacman::p_load(tidyverse,patchwork,here, pander, latex2exp)
purrr::walk(here::here(c("Functions/Display_Functions.R", "Functions/alm_core.R","Functions/misc_model_funs.R")),source)
select <- dplyr::select; mutate <- dplyr::mutate

@@

i1 <- ds |> filter(id=="3")

@@

purrr::walk(c("con_group_exam_fits", "var_group_exam_fits", "hybrid_group_exam_fits"), 
            ~ list2env(readRDS(here::here(paste0("data/model_cache/", .x, ".rds"))), 
            envir = .GlobalEnv))
```

@@

```{r}
#| label: tbl-e1-cogmodel
#| tbl-cap: Fit Parameters and Model RMSE. The Test_RMSE column is the main performance indicator of interest, and represents the RMSE for just the testing data. The Fit_Method column indicates the data used to fit the model.
#| column: screen-inset-right
#|

create_combined_df <- function(model_names, model_data, group) {
  do.call(rbind, Map(function(name, data) {
    model<- ifelse(grepl("Hybrid", name), "Hybrid", ifelse(grepl("EXAM", name), "EXAM", "ALM"))
    fit_method <- gsub(".*(Test Only|Test & Train|Train Only).*", "\\1", name)
    extract_params(model, data, group, fit_method)
  }, model_names, model_data))
}

# Adjust the extract_params function to accept and include the fit_method parameter
extract_params <- function(model_name, model_data, group, fit_method) {
  params_df <- cbind(Model = model_name, Group = group, Fit_Method = fit_method,
                     pluck(model_data, "Fit"), pluck(model_data, "test") %>% summarise(Test_RMSE = round(RMSE(y, pred)),1)) %>% 
                     mutate(across(where(is.numeric), round, 4))
  if (!"w" %in% names(params_df)) {
    params_df$w <- NA
  }
  return(params_df)
}

model_classes <- c("ALM", "EXAM", "Hybrid")
groups <- c("V", "C")

model_names_v <- c("ALM Test Only", "ALM Test & Train", "ALM Train Only", "EXAM Test Only", "EXAM Test & Train", "EXAM Train Only", "Hybrid Test Only", "Hybrid Test & Train", "Hybrid Train Only")

#model_names_v <- c("Test Only", "Test & Train", "Train Only")
model_names_c <- model_names_v

@@

combined_params_v <- create_combined_df(model_names_v, model_data_v, "Varied")
combined_params_c <- create_combined_df(model_names_c, model_data_c, "Constant")

all_combined_params <- rbind(combined_params_v, combined_params_c)

library(flextable)

identity <- function (x){x}
fmt_iden <- function(x, digits = 2) {
  paste0(x)
}

# all_combined_params %>% 
#   group_by(Group, Model) |> summarise(across(c(c,lr,Test_RMSE), ~max(.x,na.rm=TRUE)))

grouped_params <- all_combined_params %>% 
  group_by(Group, Model) %>%
  summarise(across(c(c, lr, w, Value, Test_RMSE), ~identity(.x))) %>%
  ungroup()

ft <- flextable(all_combined_params) %>% 
  theme_vanilla() %>% 
  align(align = "left", part = "all") %>% 
  colformat_double(digits = 2) %>% 
  autofit()

# Pre-calculate the averages and standard deviations
all_combined_params2 <- all_combined_params %>%
  group_by(Fit_Method, Group, Model) %>%
  summarise(
    c_stats = fmt_iden(c),
    lr_stats = fmt_iden(lr),
     rmse_stats = fmt_iden(Test_RMSE),
    .groups = "drop"
  )

# Use the pre-calculated stats in tabulator
tab <- tabulator(
  x = all_combined_params2, rows = c("Fit_Method", "Model"),
  columns = "Group",
  `c` = as_paragraph(c_stats),
  `lr` = as_paragraph(lr_stats),
  `Test_RMSE` = as_paragraph(rmse_stats)
) %>%
  as_flextable() |> align(align="left",part="all")

tab

# a=aggregate(c ~ Group+Model+Fit_Method, data=all_combined_params,identity)
# 
# all_combined_params |> group_by(Model, Group,Fit_Method) %>% 
#   summarise(
#     across(
#       all_of(c("c", "lr")),
#       list(
#         c = ~ identity(.x),
#         lr = ~ identity(.x)
#       )
#     )
#   ) %>% flextable() %>% separate_header()
# 
# 
# ft_1 <-  tabulator(
#   x = all_combined_params,
#   rows = "Group",
#   columns = c("Fit_Method","Model"),
#   `c1` = c,
#   `$lr$` = as_paragraph(lr) ) %>% as_flextable()
# 
# ft_1
```

```{r}
#| label: tbl-e1-hybridParam
#| tbl-cap: Hybrid Model - w parameter. The $w$ parameter determines the balance between the ALM and EXAM response generation processes, and is only included for the hybrid model. A weight of .5 would indicate equal contribution from both models. $w$ values approaching 1 indicate stronger weight for EXAM.

extract_params <- function(model_name, model_data) {
  cbind(Model = model_name,
        pluck(model_data, "Fit"),
        pluck(model_data, "test") %>% summarise(Test_RMSE = RMSE(y, pred))
       ) %>%
  mutate(across(where(is.numeric), \(x) round(x, 3)))
}

# Define model names and data
# model_names <- c("ALM Test Only", "ALM Test & Train", "ALM Train Only", "EXAM Test Only", "EXAM Test & Train", "EXAM Train Only", "Hybrid Test Only", "Hybrid Test & Train", "Hybrid Train Only")
# model_data_v <- list(a_te_v, a_tetr_v, a_tr_v, ex_te_v, ex_tetr_v, ex_tr_v, hybrid_te_v, hybrid_tetr_v, hybrid_tr_v)
# model_data_c <- list(a_te_c, a_tetr_c, a_tr_c, ex0_te_c, ex0_tetr_c, ex0_tr_c, hybrid_te_c, hybrid_tetr_c, hybrid_tr_c)

# params_list_v <- Map(extract_params, model_names, model_data_v)
# params_list_c <- Map(extract_params, model_names, model_data_c)

# almParamsV <- do.call(rbind, params_list_v[1:3])
# examParamsV <- do.call(rbind, params_list_v[4:6])
# hybridParamsV <- do.call(rbind, params_list_v[7:9])

# almParamsC <- do.call(rbind, params_list_c[1:3])
# examParamsC <- do.call(rbind, params_list_c[4:6])
# hybridParamsC <- do.call(rbind, params_list_c[7:9])

all_combined_params |> filter(Model =="Hybrid") |> 
  group_by(Group, Fit_Method) |>
  summarise(w=fmt_iden(first(w)), Test_RMSE=(fmt_iden(Test_RMSE))) |>
  group_by(Group,Fit_Method) |> flextable()

>>>>

```{r}
# load and view data
pacman::p_load(tidyverse,patchwork,here, pander, latex2exp, flextable)
purrr::walk(here::here(c("Functions/Display_Functions.R", "Functions/alm_core.R","Functions/misc_model_funs.R")),source)
select <- dplyr::select; mutate <- dplyr::mutate

@@

#i1 <- ds |> filter(id=="3")

@@

purrr::walk(c("con_group_exam_fits", "var_group_exam_fits", "hybrid_group_exam_fits"), 
            ~ list2env(readRDS(here::here(paste0("data/model_cache/", .x, ".rds"))), 
            envir = .GlobalEnv))

# pluck(ex_te_v, "Fit") |> mutate(w= ifelse(exists("w"), round(w,2),NA))
# pluck(hybrid_te_v, "Fit") |> mutate(w= ifelse(exists("w"), round(w,2), NA))
```

@@

```{r}
#| label: tbl-e1-cogmodel
#| tbl-cap: Fit Parameters and Model RMSE. The Test_RMSE column is the main performance indicator of interest, and represents the RMSE for just the testing data. The Fit_Method column indicates the data used to fit the model.
#| column: screen-inset-right
#| 
create_combined_df <- function(model_names, model_data, group) {
  combined_df <- do.call(rbind, Map(function(name, data) {
    model<- ifelse(grepl("Hybrid", name), "Hybrid", ifelse(grepl("EXAM", name), "EXAM", "ALM"))
    fit_method <- gsub(".*(Test Only|Test & Train|Train Only).*", "\\1", name)
    extract_params(model, data, group, fit_method)
  }, model_names, model_data))
  row.names(combined_df) <- NULL
  combined_df
}

# Adjust the extract_params function to accept and include the fit_method parameter
extract_params <- function(model_name, model_data, group, fit_method) {
  params_df <- cbind(Model = model_name, Group = group, Fit_Method = fit_method,
                     pluck(model_data, "Fit"), pluck(model_data, "test") |>
                     summarise(Test_RMSE = round(RMSE(y, pred),0))) |>
                     mutate(across(where(is.numeric), \(x) round(x, 3))) |>
                     mutate(w= ifelse(exists("w"), round(w,2), NA))
  return(params_df)
}

model_classes <- c("ALM", "EXAM", "Hybrid")

model_names <- c("ALM Test Only", "ALM Test & Train", "ALM Train Only", "EXAM Test Only", "EXAM Test & Train", "EXAM Train Only", "Hybrid Test Only", "Hybrid Test & Train", "Hybrid Train Only")

@@

combined_params_v <- create_combined_df(model_names, model_data_v, "Varied")
combined_params_c <- create_combined_df(model_names, model_data_c, "Constant")
all_combined_params <- rbind(combined_params_v, combined_params_c)

ft <- all_combined_params %>% select(-Value) |>
  rename("Fit Method" = Fit_Method, "Test RMSE" = Test_RMSE) |>
  pivot_longer(cols=c(c,lr,w,"Test RMSE"),names_to="Parameter") |>
    unite(Group, Group, Parameter) %>%
     pivot_wider(names_from = Group, values_from = value) %>%
     flextable::as_flextable() %>%
     ftExtra::span_header(sep = "\\_") |> align(i=1,align='center',part="header") |> 
  empty_blanks()  %>% 
  hline(part = "header", i = 1, j=3:6) %>% 
  hline(part = "header", i = 1, j=7:10)
ft
```

```{r}
#| column: screen-inset-right
# Reshape all_combined_params
reshaped_df <- all_combined_params %>%
  select(-Value) |>
  rename("Fit Method" = Fit_Method, "Test RMSE" = Test_RMSE) |>
  pivot_longer(cols=c(c,lr,w,"Test RMSE"),names_to="Parameter") |>
  unite(Group, Group, Parameter) %>%
  pivot_wider(names_from = Group, values_from = value)

header_df <- data.frame(
  col_keys = c("Model", "Fit Method", "Varied_c", "Varied_lr", "Varied_w", "Varied_Test RMSE", 
               "Constant_c", "Constant_lr", "Constant_w", "Constant_Test RMSE"),
  line1 = c("", "", "Varied", "", "", "", "Constant", "", "", ""),
  line2 = c("Model", "Fit Method", "c", "lr", "w", "Test RMSE", "c", "lr", "w", "Test RMSE")
)

# Apply the custom header to the flextable
ft2 <- flextable(reshaped_df) %>% 
  set_header_df(
    mapping = header_df,
    key = "col_keys"
  ) %>% add_header_lines(values = " ") %>%
  theme_booktabs() %>% 
  merge_v(part = "header") %>% 
  merge_h(part = "header") %>%
  merge_h(part = "header") %>%
  align(align = "center", part = "all") %>% 
  autofit() %>% 
  empty_blanks() %>% 
  fix_border_issues() %>% 
  hline(part = "header", i = 2, j=3:6) %>% 
  hline(part = "header", i = 2, j=7:10)

# Display the flextable
ft2

```{r}
#| column: screen-inset-right
#| 
flextable_to_markdown <- function(ft) {
  header <- ft$header$dataset %>% `rownames<-`( NULL )  %>% `colnames<-`( NULL )
  body <- ft$body$dataset %>% `rownames<-`( NULL )  %>% `colnames<-`( NULL )
  col_names <- paste0("V", 1:ncol(header))
  colnames(header) <- col_names
  colnames(body) <- col_names
  combined_df <- rbind(header, body) %>% `rownames<-`( NULL )  %>% `colnames<-`( NULL )
  markdown_table_k <- knitr::kable(combined_df, format="markdown")
  markdown_table_p <- pander::pandoc.table(combined_df,style="rmarkdown", split.table = Inf)
  return(tibble::lst(markdown_table_k,markdown_table_p))
}
flextable_to_markdown(ft)

```{r}
#| label: tbl-e1-hybridParam
#| tbl-cap: Hybrid Model - w parameter. The $w$ parameter determines the balance between the ALM and EXAM response generation processes, and is only included for the hybrid model. A weight of .5 would indicate equal contribution from both models. $w$ values approaching 1 indicate stronger weight for EXAM. 
#| eval: false
all_combined_params |> filter(Model =="Hybrid") |> 
  group_by(Group, Fit_Method) |>
  summarise(w=fmt_iden(first(w)), Test_RMSE=(fmt_iden(Test_RMSE))) |>
  group_by(Group,Fit_Method) |> flextable()
